%!TEX root = ../vrrelint.tex
% Methodology
% 300 Words

The goal of this study was to gain insight into a subjective phenomenon, how people experience intimacy and relationships in \gls{vr}.
In other words, it could be summarized as the following research question: How do people experience intimacy in \gls{vr}?


\subsection{Research Design}

Intimacy and relationships are subjective experiences. Given the goal of understanding the essence of intimacy in \gls{vr}, I followed a phenomenological approach to attempt to extract social meaning and describe the essence of the phenomenon.
Bracketing, \ie the process of setting aside personal beliefs and preconceptions, was employed.

Verbatim transcriptions of one-to-one interviews were the only data-source for this study. This was selected as it fits with the ambient of the game, which makes it easy to strike informal conversation and leverage the feeling of relative anonymity.
Avoiding priming during the interview was a concern, in this regard, I split the interview in two broad categories, a more covert portion attempting to direct the participant towards relationships in hopes of having them voluntarily talk about intimacy, followed by a more direct open ended portion. This structure was selected to attempt to balance the risk of priming and the relevance / focus of the conversation.


\subsection{Data Collection}
To extract common meaning from the lived experience of the participants, and following the principles of phenomenology, I interviewed the participants one-to-one in \vrc.

The interview followed a semi-structured approach, with the intent of guiding the participant to describe and talk about instances of intimacy in \gls{vr}, and how they experienced them, as well as their views on the generic topic of intimacy in the game. The questions and prompts I used to direct the interview were as follows:
\begin{enumerate}
	\item\label{interview::covert::motivation} What got you interested in playing \vrc? Has that motivation changed?
	\item\label{interview::covert::interactions} Do you enjoy interacting with people in \vrc? Could you talk about memorable interactions? 
	\item\label{interview::covert::friendships} Did you make friends or establish any kind of relationship? Tell me about them.
	\item\label{interview::overt::descibemoment} Describe a moment in which you experienced intimacy in \vrc.
	\item\label{interview::overt::vrvsonline} Did the \gls{vr} medium change the experience compared to other online mediums? 
	\item\label{interview::overt::feelaboutintimacy} How do you feel about intimacy and intimate relationships in \gls{vr}?
\end{enumerate}

The objective of these lines of questioning was focusing the interview on the topic of relationships and intimacy and reduce the number of irrelevant outcomes.

Priming or influencing the participants was a concern, therefore I decided to split the interview in two parts.
In the first part, consisting of $3$ indirect prompts or lines of questioning, to mitigate the risk of influencing or priming the subject, I avoided asking the research question directly, instead asking about motivations (Question~\ref{interview::covert::motivation}), interactions (Question~\ref{interview::covert::interactions}), and developed relationships (Question~\ref{interview::covert::friendships}).
The rationale being that this line of conversation might lead the participants to talk about their relationships, how much these motivated them to spend time in \gls{vr} and how they lead to intimacy and their experience.

After this covert part of the interview, I asked some more overt questions, to focus even further, and learn how they experienced intimacy in \gls{vr} and their opinion on the topic.
In particular, following the typical phenomenological approach seen in the literature~\cite{register92}, the second part starts with an open-ended (Question~\ref{interview::overt::descibemoment}) request to describe a moment of intimacy in \vrc. 
While this is more direct, and reveals the objectives of the interview, it also leads directly to the description of relevant experiences.
Even though this second part is subject to the researcher's influence, this can be taken into account during the analysis, while still providing useful information on the participants lived experiences.


\subsection{Sample}
Video and audio data was collected from 5 interviews, totaling \todo{sum runtime} minutes of video. 
Participants were selected by approaching players in the social game, \vrc, and asking them if they were open to being interviewed and consented to recording.